---
title: "Craps Simulation"
format: html
---

```{r echo=FALSE,warning=FALSE, message=FALSE}

#setting up:
library(tidyverse)
source("play-craps.R")

```


## `The probability of winning a game of craps in exactly 3 rolls`

```{r}
# Run a large number of simulations
set.seed(123)  # For reproducibility
num_simulations <- 1000
simulation_results <- run_craps_simulation(num_simulations)

# Calculate the probability of winning in exactly 3 rolls
win_in_3_rolls <- simulation_results %>%
  filter(outcome == "win" & n_rolls == 3) %>%
  nrow()

probability_win_3_rolls <- win_in_3_rolls / num_simulations

cat("Probability of winning in exactly 3 rolls:", round(probability_win_3_rolls, 4))
```


## `The probability of winning a craps game with initial points 6 or 8`

```{r}
set.seed(456)  # seed
num_simulations <- 100
simulation_results <- run_craps_simulation(num_simulations)

# Analyze games with initial point of 6 or 8
point_6_8_games <- simulation_results %>%
  filter(point %in% c(6, 8))

# Calculate probabilities for point 6 or 8
point_6_8_analysis <- point_6_8_games %>%
  group_by(point) %>%
  summarize(
    total_games = n(),
    wins = sum(outcome == "win"),
    win_probability = wins / total_games,
    avg_rolls = mean(n_rolls)
  )

print(point_6_8_analysis)
```
## `Comparative analysis`

```{r}
# Comparative analysis with other points
point_analysis <- simulation_results %>%
  filter(point %in% c(4, 5, 6, 8, 9, 10)) %>%
  group_by(point) %>%
  summarize(
    total_games = n(),
    wins = sum(outcome == "win"),
    win_probability = wins / total_games,
    avg_rolls = mean(n_rolls)
  ) %>%
  arrange(desc(win_probability))

print(point_analysis)
```

* The most common points set were 5 (16 times) and 6 (14 times).

* Point 8 has the highest win probability at 66.7% (4 wins out of 6 games).

* Games with point 6 lasted the longest on average, with 5.86 rolls.

```{r}
# Visualize the win probabilities
library(ggplot2)

ggplot(point_analysis, aes(x = factor(point), y = win_probability, fill = factor(point))) +
  geom_bar(stat = "identity") +
  labs(
    title = "Win Probability by Initial Point in Craps",
    x = "Initial Point",
    y = "Win Probability",
    fill = "Points"
  ) +
  theme_minimal()
```

* The number of games for each point varies significantly (from 6 to 16). 

* In this simulation, setting a point of 8 appeared to be most advantageous, with the highest win rate.However, the small sample size (only 6 games) means this could be due to chance.

* Point 4 seems to be the most challenging to win, with the lowest win probability of 18.2%.

* Interestingly, there doesn't seem to be a clear correlation between the average number of rolls and the win probability. For example, point 6 has the highest average rolls but a relatively low win probability.